\documentclass[11pt,a4]{moderncv}
\input{formatting-en}

\setmainlanguage{english}

\input{contact-en}
\date{\today}
\title{DevOps Engineer}
\hypersetup{
 pdfauthor={Timur Demin},
 pdftitle={DevOps Engineer},
 pdflang={English}
}
\begin{document}

\makecvtitle

\input{education-en}

\section{Experience}
\cventry{\textbf{Dec 2021 --- Jun 2023}}{DevOps / Platform Engineer}{RN-BashNIPIneft LLC}{}{}{
    \begin{itemize}
    \item
        Upkept infrastructure in Docker / Kubernetes, kept documentation as Ansible / helmfile
        code where possible. Maintained a local Ansible role and module library for various
        administration tasks.
    \item
        Maintained internally developed systems, their deployment to test and production
        contours. Built CI/CD pipelines for them in Jenkins.
    \item
        Worked on an internal development platform (IDP) initially based on GitLab CE,
        superseded with Keycloak / Gitea / Jenkins / Nexus / Harbor / SonarQube. Maintained
        IDP-specific innerworkings: shared Jenkins libraries, Jenkins agent images, local base
        Docker image library with repository / certificates presets, etc. Maintained an older
        TeamCity instance.
    \item
        Developed IDP-specific release engineering and automation software:
        \begin{itemize}
            \item
                Gitea release uploader and changelog generator, written in Go
            \item
                Gitea group policy editor (allowing default repository settings, automatic
                branch creation, enabling branch protection, etc), written in Go
            \item
                Gitea repository batch processing utility (repository settings, user /
                repository migration between instances, etc), written in Python
        \end{itemize}
    \item
        Managed both IDP-internal (fluent-bit / Loki / Prometheus / Thanos / Alertmanager
        / Grafana) and project-specific (Logstash, Elasticsearch / Prometheus / Grafana)
        monitoring and logging services. Maintained team-specific monitoring for Oracle XE
        and PostgreSQL.
    \item
        Administered corporate YouTrack instance, developed JavaScript workflows for teams using
        YouTrack for tech support (e.g. automatic company detection for incoming tickets,
        assigning teams by task state, etc).
    \item
        Combined DevOps and backend developer roles on one of the projects: worked on
        services providing cron webhooks and container image building capabilities in Go /
        Labstack Echo / PostgreSQL / buildah.
    \item
        Provided developers with tech/tooling support where necessary.
    \end{itemize}
}
\cventry{\textbf{Jun 2020 --- Jul 2020}}{Intern}{JSC Nefteavtomatika}{}{}{
    \begin{itemize}
    \item
        Worked on internal microcontroller accounting software in Go / Gorilla /
        Pongo2 / PostgreSQL. Ensured its compatibility with Debian 9.
    \end{itemize}
}
\cventry{\textbf{2019 --- current}}{Maintainer}{tdem.in}{}{}{
    Maintaining various web services (Nextcloud, TTRSS, Gitea, Drone) for personal use.
    Set up automatic builds of Docker images with Gitea / Drone (later changed to GitHub
    Actions) for deployment to a personal server. Configured automatic backups. Made a
    GitHub Action to retrieve latest Git tags of software for automatic builds.
}

\section{Skills}
\cvitem{\bfseries General}{Linux (Ubuntu, Debian, Red Hat), Git, networking, storage}
\cvitem{\bfseries Containers}{Docker, rootless podman / buildah}
\cvitem{\bfseries CI/CD}{Jenkins, GitHub Actions, Drone CI (1.x), GitLab CI, TeamCity}
\cvitem{\bfseries Automation, IaaC}{Ansible, helmfile}
\cvitem{\bfseries Logging}{fluent-bit, Logstash, Loki}
\cvitem{\bfseries Monitoring, Alerting}{Prometheus, Thanos, Grafana}
\cvitem{\bfseries Orchestration}{Kubernetes (bare metal, k3s), docker-compose}
\cvitem{\bfseries Databases}{PostgreSQL, Redis, Elasticsearch}
\cvitem{\bfseries Backups}{restic}
\cvitem{\bfseries Development}{Go (Echo, Gorilla), Python, bash, Groovy, JavaScript / TypeScript}

\input{misc-en}

\end{document}
